Plots and tables summarizing results of Poisson simulations

### 2019-12-16 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@

```{r plot-spikes-function, fig.height=2.5, fig.width=8}
mu.s <- 0.01 + spike.f(t)
x    <- rpois(n,mu.s)
create.signal.plot(mu.s,x)
```

@@

```{r plot-angles-function, fig.height=2.5, fig.width=8}
mu.ang <- 0.01 + angles.f(t)
x      <- rpois(n,mu.ang)
create.signal.plot(mu.ang,x)
```

@@

```{r plot-heavisine-function, fig.height=2.5, fig.width=8}
mu.hs <- 0.01 + heavi.f(t)
x     <- rpois(n,mu.hs)
create.signal.plot(mu.hs,x)
```

@@

```{r plot-bursts-function, fig.height=2.5, fig.width=8}
mu.bur <- 0.01 + bursts.f(t)
x      <- rpois(n,mu.bur)
create.signal.plot(mu.bur,x)
```

@@

```{r plot-cb-function, fig.height=4, fig.width=8}
mu.cb <- 0.01 + cblocks.f(t)
x     <- rpois(n,mu.cb)
create.signal.plot(mu.cb,x)
```

@@

```{r plot-bumps-function, fig.height=4, fig.width=8}
mu.b <- 0.01 + bumps.f(t)
x    <- rpois(n,mu.b)
create.signal.plot(mu.b,x)
```

>>>>

```{r set-seed}
set.seed(1)
```

@@

```{r plot-spikes-function, fig.height=2.5, fig.width=8}
mu.s <- 0.01 + spike.f(t)
x    <- rpois(n,mu.s)
create.signal.plot(t,x,mu.s)
```

@@

```{r plot-angles-function, fig.height=2.5, fig.width=8}
mu.ang <- 0.01 + angles.f(t)
x      <- rpois(n,mu.ang)
create.signal.plot(t,x,mu.ang)
```

@@

```{r plot-heavisine-function, fig.height=2.5, fig.width=8}
mu.hs <- 0.01 + heavi.f(t)
x     <- rpois(n,mu.hs)
create.signal.plot(t,x,mu.hs)
```

@@

```{r plot-bursts-function, fig.height=2.5, fig.width=8}
mu.bur <- 0.01 + bursts.f(t)
x      <- rpois(n,mu.bur)
create.signal.plot(t,x,mu.bur)
```

@@

```{r plot-cb-function, fig.height=4, fig.width=8}
mu.cb <- 0.01 + cblocks.f(t)
x     <- rpois(n,mu.cb)
create.signal.plot(t,x,mu.cb)
```

@@

```{r plot-bumps-function, fig.height=4, fig.width=8}
mu.b <- 0.01 + bumps.f(t)
x    <- rpois(n,mu.b)
create.signal.plot(t,x,mu.b)
```
